Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-31 paper.tex

\section{System Architecture}
Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade in streaming data subscription.

>>>>

\section{System Architecture}
Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade in streaming data subscription.
